
% {{{ preamble

\documentclass[12pt,letterpaper]{article}

\usepackage{url}
\usepackage{hyperref}

\usepackage{graphicx}

\usepackage{vmargin}  % make the margins a bit smaller
\setmarginsrb{1.0in}{1.0in}{1.0in}{1.0in}{0in}{0.4in}{0.0in}{0.40in}

\raggedright
%\setlength{\parindent}{0.5in}
%\noindent
\usepackage{parskip}

\usepackage{sectsty}
\sectionfont{\large}

% no numbers in bibliography, good
\usepackage[backend=biber,autocite=footnote,
			bibstyle=authortitle,citestyle=verbose-inote]{biblatex}
% big numbers, no foot note citations
%\usepackage[backend=biber,style=numeric]{biblatex} % OK
% bibliography numbers different than footnote number
%\usepackage[backend=biber,autocite=footnote,
%			bibstyle=numeric,citestyle=verbose-inote]{biblatex}
%\usepackage[backend=biber,autocite=footnote,
%			bibstyle=numeric,citestyle=verbose-inote]{biblatex}  % OK

\addbibresource{refs.bib}

% }}}

\renewcommand*{\theenumi}{\thesection.\arabic{enumi}}
\renewcommand*{\theenumii}{\theenumi.\arabic{enumii}}

\begin{document}

% {{{ title page
\vspace*{1.0in}

\centerline{\LARGE \textbf{SprinklerPI}}
\vspace{0.3in}
\centerline{\LARGE Product Concept}

\vfill

\begin{center}
\begin{tabular}{c}
Jeremiah Mahler \\
EECE 490B, CSU Chico \\
May 6, 2014
\end{tabular}
\end{center}

\vspace{2in}

\thispagestyle{empty}

\pagebreak
% }}}

\tableofcontents
\addtocontents{toc}{~\hfill{Page}\par}
\pagebreak

% {{{ Executive Summary
\pagebreak
\section{Executive Summary}

This project is a sprinkler timer for watering lawns and plants
on a regular schedule.
It is network accessible and can be configured through a web browser.
The system is also expandable.
It can control from one valve to several hundred valves.

% users
The primary user of this project would be a homeowner who has
lawns or other plants that need watering on a regular schedule.
Businesses with landscaping that needs watering could also use
this system.

The system will need to be installed by someone familiar with
irrigation systems (timers and valves).
Since this system is network accessible it will need to be initially
configured by someone familiar with Ethernet and Wireless networks.

After installation anyone should be capable of configuring the
water schedule through the web based interface.

% environmental impact
This project has a positive environmental impact as a result of the
more efficient use of water resources.

It is estimated that this project will take four months to complete.
It is estimated that the hardware will cost approximately \$225.

% }}}

\pagebreak

% {{{ Product Users
\section{Product Users}

\begin{enumerate}
\item Homeowners that have landscaping that needs watering.
\item Business owners that have landscaping that needs watering.
\item Anyone familiar with home irrigation systems (timers, valves)
should be capable of installing the system.
\item Anyone familiar with Ethernet and Wireless networks should
	be capable of configuring the network.
\item Anyone should be able to configure the watering schedule.
\end{enumerate}

% }}}

% {{{ Environmental and Social Impact of Project
\section{Environmental Impact}

\begin{enumerate}
\item More efficient use of water resources.
\end{enumerate}

\section{Social Impact}

This project has no significant social impact.

% }}}

% {{{ Assumptions, Dependencies, and Constraints
\section{Assumptions, Dependencies, and Constraints}

\begin{enumerate}
\item A RasberryPI board will be available.
\end{enumerate}

% }}}

% {{{ User Accessible Features
\begin{samepage}
\section{User Accessible Features}

\begin{enumerate}
\item Web interface accessible using a web browser.
	\begin{enumerate}
	\item Schedule valve run times.
	\item Manually start/stop valves.
	\end{enumerate}
\item Hardware interface (at timer).
	\begin{enumerate}
	\item Indicator when power is applied.
	\item Indicator when a valve is on.
	\end{enumerate}
\end{enumerate}
\end{samepage}

% }}}

% {{{ Estimate Project Costs
\begin{samepage}
\section{Estimated Project Costs}

\begin{enumerate}
\item RasberryPI\autocite{rpi} with case and cables (\$50).
\item Power supply PCB (assembled) (\$17).
\item Control/Driver PCB (assembled, x3) (\$69).
\item Enclosure (\$35).
\item Miscellaneous wiring and connectors (\$50).
\end{enumerate}

\textbf{TOTAL: \$221}\footnote{It is estimated that switching
to SMD components instead of through hole would halve the total cost.}
\end{samepage}
% }}}

\pagebreak
\printbibliography[heading=bibintoc]

\end{document}
